---
title: "London Families Interactive Report (Trial)"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: spacelab # yeti is also nice
  
# This code is inspired by Matt Dray's example using education data
# https://matt-dray.github.io/earl18-crosstalk/04_leaflet-flexdash-dt-crosstalk.html
---

```{r setup, include=FALSE}

## Prepare the workspace

library(flexdashboard)
library(bslib)
library(leaflet)
library(DT)
library(crosstalk) 
library(dplyr)
library(popmodules)
library(gglaplot)
library(ggplot2)
library(data.table)
library(tidyr)
library(png)
library(stringr)
library(tidyverse)
library(plotly)
library(sf)
library(htmlwidgets)
library(ggplot2)
library(gglaplot)
library(glaly)
library(knitr)
library(leaflet.extras)
library(leaflegend)
library(leaflet.providers)
library(lubridate)
library(maps)
library(scales)
library(forcats)

data_dir <- 'DATA/'

```



```{r datamanip, include=FALSE}

#---------------------------------------------------------
#THIS CODE COULD GO INTO DATAMANIP FILE

# input data about dispersal, pledges, UASC and population
input_peopledata <- fread(paste0(data_dir,"People_Data_all_ed.csv"))%>% 
  data.frame()

# Import borough boundaries
borough_boundaries<-
  st_read(paste0(data_dir,"London_Borough_Excluding_MHW.shp"))

# For leaflet map, change projection from GB OS grid to the standard World Geodetic System which uses lats and longs.
boroughs_WGS84 <- st_transform(borough_boundaries, 4326)

# Match with geographical data, create categories for mapping and drop unwanted variables
Data_geog_WGS84 <- boroughs_WGS84%>% 
  left_join(input_peopledata, by=c("GSS_CODE"="BoroughCode"))%>%
  mutate(DispersalCat = cut(Rate_of_DA, breaks = c(-1, 0, 35, 70, 140, 300),
                           labels = c("1", "2", "3", "4", "5"))) %>%
  mutate(UASC_Colour = recode(UASC_Col, 
                              "Green" = "1", 
                              "Amber" = "2", 
                              "Red" = "3", 
                              "Purple" = "4")) %>%
  mutate(PopCat = cut(Pop_total_2020, breaks = c(-1, 100000, 200000, 300000, 400000),
                           labels = c("1", "2", "3", "4"))) %>%
  select(!c("HECTARES", "BoroughName", "NONLD_AREA", "ONS_INNER", "SUB_2009", "SUB_2006")) 

# add unique ID to each row to help with matching
Data_geog_WGS84 <- tibble::rowid_to_column(Data_geog_WGS84, "index")

# Create centroids for mapping using coordinates of lats and longs, and create index for matching  
cent <- st_transform(Data_geog_WGS84, crs = 4326) %>%
  st_centroid() %>% 
  st_geometry() %>% 
  as_tibble() %>% # convert list to tibble 
  extract(geometry, c('long', 'lat'), '\\((.*), (.*)\\)', convert = TRUE) %>%
  rowid_to_column("index")

# Merge original data file with new centroid data
Data_geog_WGS84_cent <- merge(Data_geog_WGS84, cent, by="index")

# Convert data for use in DT and crosstalk
shared_migration_data <- SharedData$new(Data_geog_WGS84_cent)

#--------------------------------------------------------------------------

## Provide extra info for choropleth maps

# For dispersal map
catblue5 = c('#eeeeee', '#a6bbd4', '#6e88a6', '#44586f', '#252c35')

catnames_new <- c("0", "1-34", "35 - 69", "70-139", "140-300")

mypalette2 <- colorFactor(catblue5,
                          levels = c("1", "2", "3", "4", "5"),
                          ordered = FALSE,
                          na.color = "#808080",
                          alpha = FALSE,
                          reverse = FALSE)
# For UASC map
UASC_catcolor = c("#7fc97f", "#fdc086", "#fb8072") # no need for "#7570b3"

#7fc97f is green, #fdc086 is orange and #fb8072 is red (no need for purple)

UASC_catnames <- c("Below 0.07%", "0.07 - 0.09%", "> or = 0.10%")

mypalette3 <- colorFactor(UASC_catcolor,
                          levels = c("1", "2", "3"),
                          ordered = FALSE,
                          na.color = "#808080",
                          alpha = FALSE,
                          reverse = FALSE)

# For population map (currently not included)
catgreen4 = c('#eeeeee', '#acc1aa', '#739272', '#4a6349')

popCat_names <- c("0 - 99K", "100 - 199K", "200 - 299K", "300 - 400K")

mypalette4 <- colorFactor(catgreen4,
                          levels = c("1", "2", "3", "4"),
                          ordered = FALSE,
                          na.color = "#808080",
                          alpha = FALSE,
                          reverse = FALSE)

```

Schools {data-icon="ion-home"}
=====================================  

### Name of topic being mapped

Row {data-height=500}
-----------------------------------------------------------------------

### First Interactive Line chart - primary schools numbers over time

```{r chart1}

```

### Second Interactive Line chart - secondary schools numbers over time

```{r chart2}

```

Row {data-height=500}
-----------------------------------------------------------------------

### First Interactive map - primary schools change

```{r map1}

```

### Second Interactive map - secondary schools change

```{r map2}


```

Total fertility rate {data-navmenu="🕮 Births" data-icon="ion-stats-bars"}
=====================================  

### 

Row {data-height=500}
-----------------------------------------------------------------------

### First Interactive Line chart - Births over time

```{r chart3}


```

### Second Interactive Line chart - TFR over time

```{r chart4}


```
Row {data-height=500}
-----------------------------------------------------------------------

### Third Interactive Line chart - Number of potential mothers over time

```{r chart5}


```
### First Interactive map - TFR now

```{r map3}

## Map for Dispersal accomodation

dispersal_map <- leaflet(shared_migration_data) %>% 
  setView(lng = -0.1181 , lat = 51.51, zoom = 9) %>% # 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~mypalette2(DispersalCat),
                 weight = 0.5,
                 opacity = 1,
                 color = "black",
                fillOpacity = 0.7) %>%
  addLegend("bottomleft", 
            colors = catblue5, 
            values = DispersalCat, 
            labels = catnames_new, title = "Dispersed acc., Asylum seekers/100,000 residents") %>%
  addAwesomeMarkers(data = shared_migration_data, 
             lng =  ~ long, lat = ~ lat, 
               popup = ~paste0(
       "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
      
      "<table style='width:100%'>",
      
      "<tr>",
      "<th>Number in dispersal</th>",
      "<th>", Data_geog_WGS84_cent$SeekingAsylum_InDispersal,"</tr>",
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Borough population</th>",
      "<th>", format(Data_geog_WGS84_cent$Pop_total_2020, big.mark = ",", scientific = FALSE)  ,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Rate of dispersal accomodation<br>per 100,000 residents</th>",
      "<th>", Data_geog_WGS84_cent$Rate_of_DA, "</tr>",
      "</tr>"
          ),  # end popup()
    icon = awesomeIcons(
      library = "ion",
      icon = "ion-android-radio-button-on",
      iconColor = "white",
      markerColor = ifelse(
        test = Data_geog_WGS84_cent$Inner == 1, 
        yes = "red",
        no = "blue")
      )
    )    # end addAwesomeMarkers()
dispersal_map

```

Fertility {data-navmenu="🕮 Births" data-icon="ion-connection-bars"}
=====================================  

### ASFR

Row {data-height=500}
-----------------------------------------------------------------------
### First Interactive Line chart - ASFR over time

```{r chart6}


```

### Second Interactive Line chart - SMA over time

```{r chart7}


```
Row {data-height=500}

-----------------------------------------------------------------------
### First Interactive map - TFR

```{r map4}

UASC_map <- leaflet(shared_migration_data) %>% 
  setView(lng = -0.1181 , lat = 51.51, zoom =9) %>% # 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~mypalette3(UASC_Colour),
                 weight = 0.5,
                 opacity = 0.8,
                 color = "black",
                fillOpacity = 0.5) %>%
  addLegend("bottomleft", 
            colors = UASC_catcolor, 
            values = UASC_Cat, 
            labels = UASC_catnames , title = "UASC Categories: 0.07% Threshold")%>%
  addAwesomeMarkers(data = shared_migration_data, 
             lng =  ~ long, lat = ~ lat, 
               popup = ~paste0(
       "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
      
      "<table style='width:100%'>",
      
      "<tr>",
      "<th>UASC in borough</th>",
      "<th>", Data_geog_WGS84_cent$UASC,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Borough <18 y.o. population</th>",
      "<th>", format(Data_geog_WGS84_cent$Pop_child_2020, big.mark = ",", scientific = FALSE),
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Rate of UASC<br>per 100 children</th>",
      "<th>", format(round(Data_geog_WGS84_cent$UASC_Rate, 2)), "</th>",
      "</tr>"
          ),  # end popup()
    icon = awesomeIcons(
      library = "ion",
      icon = "ion-android-radio-button-on",
      iconColor = "white",
      markerColor = ifelse(
        test = Data_geog_WGS84_cent$Inner == 1, 
        yes = "red",
        no = "blue")
      )
    )    # end addAwesomeMarkers()
UASC_map
```
### Second Interactive map - SMA

```{r map5}

UASC_map <- leaflet(shared_migration_data) %>% 
  setView(lng = -0.1181 , lat = 51.51, zoom =9) %>% # 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~mypalette3(UASC_Colour),
                 weight = 0.5,
                 opacity = 0.8,
                 color = "black",
                fillOpacity = 0.5) %>%
  addLegend("bottomleft", 
            colors = UASC_catcolor, 
            values = UASC_Cat, 
            labels = UASC_catnames , title = "UASC Categories: 0.07% Threshold")%>%
  addAwesomeMarkers(data = shared_migration_data, 
             lng =  ~ long, lat = ~ lat, 
               popup = ~paste0(
       "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
      
      "<table style='width:100%'>",
      
      "<tr>",
      "<th>UASC in borough</th>",
      "<th>", Data_geog_WGS84_cent$UASC,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Borough <18 y.o. population</th>",
      "<th>", format(Data_geog_WGS84_cent$Pop_child_2020, big.mark = ",", scientific = FALSE),
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Rate of UASC<br>per 100 children</th>",
      "<th>", format(round(Data_geog_WGS84_cent$UASC_Rate, 2)), "</th>",
      "</tr>"
          ),  # end popup()
    icon = awesomeIcons(
      library = "ion",
      icon = "ion-android-radio-button-on",
      iconColor = "white",
      markerColor = ifelse(
        test = Data_geog_WGS84_cent$Inner == 1, 
        yes = "red",
        no = "blue")
      )
    )    # end addAwesomeMarkers()
UASC_map

```


Migration  {data-icon="ion-person-stalker"}
=====================================  

### Name of topic being mapped

Row {data-height=250}
-----------------------------------------------------------------------

### Filters

```{r filters3}

```

Row {data-height=750}
-----------------------------------------------------------------------

### Interactive map

```{r map3}

```

### Datatable

```{r datatable3}

```

Housing Pressures {data-icon="ion-home"}
=====================================  

### Name of topic being mapped

Row {data-height=250}
-----------------------------------------------------------------------

### Filters

```{r filters4}

```

Row {data-height=750}
-----------------------------------------------------------------------

### Interactive map

```{r map4}

```

### Datatable

```{r datatable4}

```


Hotels {data-icon="ion-briefcase"}
=====================================  

### HOTELS

Row {data-width=300}
-----------------------------------------------------------------------

### Interactive map

```{r map5}

hotels_map <- leaflet(shared_hotel_data) %>% 
  setView(lng = -0.1181 , lat = 51.51, zoom =10) %>% 
  addPolygons(data = Data_geog_WGS84_cent,
    fillColor = "white",
    weight = 0.5,
    opacity = 1,
    color = "black",
    fillOpacity = 0.5)%>%
  addCircles(data = input_initialpostcodes, 
             lng =  ~ long, lat = ~ lat, 
             color = 'black',
             #stroke = FALSE,  # this removes outlines to circles
             fillColor = 'green', # Yellow
             fillOpacity = 0.5,
             weight = 1,
             opacity = .8, # use fillOpacity = 0 if just want outlines
             radius=~Extra_people*3) %>%
#             popup=popupInitial,
#             popupOptions = popupOptions(closeOnClick = TRUE)) %>%
  addCircles(data = input_bridgingpostcodes, 
             lng =  ~ long, lat = ~ lat, 
             color = 'black',
             #stroke = FALSE,  # this removes outlines to circles
             fillColor = '#dee000', # Yellow
             weight = 1,
             fillOpacity = 0.5,
             opacity = .8, # use fillOpacity = 0 if just want outlines
             radius=~Number_in_Hotel*2) %>%
#             popup=popupBridging,
#             popupOptions = popupOptions(closeOnClick = TRUE)) %>%
  addCircles(data = input_asylumpostcodes, 
             lng =  ~ long, lat = ~ lat, 
             color = 'black',
             #stroke = FALSE,  # this removes outlines to circles
             fillColor = '#9e0059', # Red
             fillOpacity = 0.5,
             weight = 1,
             opacity = .8, # use fillOpacity = 0 if just want outlines
             radius=~Service_Users*2)%>%
#             popup=popupAsylum,
#             popupOptions = popupOptions(closeOnClick = TRUE)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% # an alternative is $Esri.NatGeoWorldMap
  #addTiles() %>% # default is OpenStreetMap
  addLegendSize(position = "topright",
                values = input_initialpostcodes$Extra_people, 
                color = 'black',
                fillColor = 'green',
                opacity = .5,
                title = 'Initial accomodation sites, No. residents (approx)',
                shape = 'circle',
                orientation = 'vertical',
                baseSize = 10,
                breaks=1) %>%
  addLegendSize(position = "topright",
              values = input_bridgingpostcodes$Service_Users, 
              color = 'black',
              fillColor = '#dee000', # Yellow
              opacity = .5,
              title = 'Afghan Bridging Hotels, No. bedspaces',
              shape = 'circle',
              orientation = 'vertical',
              baseSize = 10,
                  breaks=3)%>%
  addLegendSize(position = "bottomright",
                values = input_asylumpostcodes$Service_Users, 
                color = 'black',
                fillColor = '#9e0059', # Red
                opacity = .5,
                title = 'Asylum contingency hotels, No. residents',
                shape = 'circle',
                orientation = 'vertical',
                baseSize = 10,
                breaks=3)%>%
    addCircleMarkers(data = shared_hotel_data, # this to to add popups without markers
             lng =  ~ long, lat = ~ lat, 
             stroke = FALSE,  # this removes outlines to circles
             fillOpacity = 0, # this removes the fill
             popup = ~paste0(
       "<h4>", input_hotelData$Hotel.Name, "</h4>",
      
      "<table style='width:100%'>",
   
      "<tr>",
      "<th>Post code</th>",
      "<th>", input_hotelData$Postcode,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Borough</th>",
      "<th>", input_hotelData$LA,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Type of hotel</th>",
      "<th>", input_hotelData$Type,
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Service Users</th>",
      "<th>", input_hotelData$Service_Users_All, "</th>",
      "</tr>"
          )
      )
hotels_map

```


Data (all) table {data-icon="ion-grid"}
=====================================  

### Dataset for "Fair Shares" Model

Row {data-height=250}
-----------------------------------------------------------------------
### Filters

```{r filters6}

# Convert data for use in DT and crosstalk

input_Table_Data <- fread(paste0(data_dir,"Table_Data.csv"))%>% 
  data.frame()

shared_Table_Data <- SharedData$new(input_Table_Data)

bscols(widths = c(3,NA),  
       list(
  filter_select(
  id = "BoroughName",
  label = "_Borough",
  sharedData = shared_Table_Data, 
  group = ~BoroughName
  )
),  
filter_checkbox(
    id = "Inner",
    label = "Zone of Greater London",
    sharedData = shared_Table_Data,
    ~ifelse(Inner == 1, "Inner", "Outer")
))
#filter_slider(
#    id = "UASC",
#    label = "Number of Unaccompanied Children",
#    sharedData = shared_migration_data,
#    column = ~UASC,
#    step = 10,
#    round = TRUE,
#    sep = "",
#    ticks = FALSE
#),
#filter_slider(
#    id = "Pop_child_2020",
#    label = "Number of children under 18 y.o. in borough",
#    sharedData = shared_migration_data,
#    column = ~Pop_child_2020,
 #   step = 1,
#    round = TRUE,
#    sep = "",
 #   ticks = FALSE
# ))
```

Row {data-height=750}
-----------------------------------------------------------------------

### Data Table

```{r datatable6}

shared_Table_Data  %>% 
  DT::datatable(
 #   filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons",  # add download buttons, etc
      "Scroller"  # for scrolling down the rows rather than pagination
    ),
    fillContainer = FALSE, 
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    class = "compact",
    width = "100%",
    options = list(
      dom = "Blrtip",  # specify content (search box, etc)
        # B = Buttons
        # l - length changing input control
        # r - processing display element
        # t - The table!
        # i - Table information summary
        # p - pagination control
      deferRender = TRUE, # speeds initialisation
      scrollY = 300, # for vertical scrolling
      scrollX = TRUE,
      fixedColumns = list(leftColumns = 0),
      scroller = TRUE, 
      buttons = list(
        I("colvis"),  # turn columns on and off
        "copy", 
        "print", list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'
      ))
    ),
    colnames = c(
      "Borough" = "BoroughName",
      "Pledge" = "MidPledge",
      "Dispersed" = "SeekingAsylumInDispersal",
      "In hotel" = "SeekingAsylumInHotels",
      "UASC in care" = "UASCinCare",
      "Resettled" = "RefugeesResettled"
    )
  )
```


Information {data-orientation=columns  data-icon="ion-information-circled"}
===================================== 


Column {data-width=333}
-----------------------------------------------------------------------

### Background

Central government is working with local authorities to develop a full asylum dispersal model, supported by grant funding. It has been agreed that regional allocations will be based on population data, but the regions can develop their own individual regionsal dispersal models if they wish.

London Councils have been working with boroughs and the London Strategic Migration Partnership to develop a draft model for the London regional dispersal plan. 

All partners concur that allocations should use a "place-based approach", meaning being sensitive to local contexts, and having a joined up ask of councils and their partners across different Home Office schemes, especially resettlement, asylum dispersal and the National Transfer Scheme. 

Thus this interactive report has been developed by the GLA with the following goals - to <br>
1) facilitate the implementation and maintenance of a ‘fair share’ approach across London to the support of refugee and people seeking asylum, and <br>
2) enable the funding and development of services that are ‘place based’ to maximise opportunities for support and social integration available for these groups.







Column {data-width=333}
-----------------------------------------------------------------------
### How to use 

#### Filters

You can:

* Select one or more boroughs from the dropdown menu (remove them with your backspace key)
* Select boroughs in inner or outer London using the checkbox
* Drag the sliders to filter boroughs by criteria such as population

#### Interactive map

You can:

* Click to grab and drag the map around
* Zoom with the ‘+’ and ‘–’ buttons (top-left) or with your mouse’s scroll wheel
* Click the button showing a broken square (top-left under the zoom options) to select points on the map using a window that’s draggable (click and hold the grid icon in the upper left) and resizeable (click and drag the white boxes in each corner)

#### Datatable

You can:

* Change which columns are visible by clicking the 'Column visibility' button
* Click 'Download' to save the filtered data to a .csv, .xlsx or .pdf file


Column {data-width=333}
-----------------------------------------------------------------------
### Tools

[R v4.1.3](https://www.r-project.org/) and [RStudio 2022.02.1](https://www.rstudio.com/) were used to build this tool.

The packages used were:

* [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) to create a frame for the content
* [Leaflet](https://rstudio.github.io/leaflet/) for the interactive map
* [DT](https://rstudio.github.io/DT/) for the interactive table
* [Crosstalk](https://rstudio.github.io/crosstalk/) for widget interactivity
* [Ion icons](https://ionicons.com/) for icons

This dashboard was inspired by that of Matt Dray, and his code provided the foundation of the code for the current dashboard.

See [github.com/matt-dray/earl18-crosstalk](https://github.com/matt-dray/earl18-crosstalk)

The code for this tool is available from: ADD LINK TO MY CODE 

For any queries:

* About the interactive report, contact Veronica.Tuffrey@london.gov.uk
* About the data, contact Mark Winterburn@london.gov.uk



