---
title: "London Families Interactive Report (Trial) on 5/6/24"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: yeti 
  
# This code is inspired by Matt Dray's example using education data
# https://matt-dray.github.io/earl18-crosstalk/04_leaflet-flexdash-dt-crosstalk.html
---

```{r setup, include=FALSE}

## Prepare the workspace

library(flexdashboard)
library(bslib)
library(leaflet)
library(DT)
library(crosstalk) 
library(dplyr)
#library(popmodules)
#library(gglaplot)
library(ggplot2)
library(data.table)
library(tidyr)
library(png)
library(stringr)
library(tidyverse)
library(plotly)
library(sf)
library(htmlwidgets)
#library(glaly)
library(knitr)
library(leaflet.extras)
library(leaflegend)
library(leaflet.providers)
library(lubridate)
library(maps)
library(scales)
library(forcats)

data_dir <- 'DATA/'

```



```{r datamanip, include=FALSE}

#---------------------------------------------------------
#THIS CODE COULD GO INTO DATAMANIP FILE

# # input data about dispersal, pledges, UASC and population
# input_peopledata <- fread(paste0(data_dir,"People_Data_all_ed.csv"))%>% 
#   data.frame()
# 
# # Import borough boundaries
# borough_boundaries<-
#   st_read(paste0(data_dir,"London_Borough_Excluding_MHW.shp"))
# 
# # For leaflet map, change projection from GB OS grid to the standard World Geodetic System which uses lats and longs.
# boroughs_WGS84 <- st_transform(borough_boundaries, 4326)
# 
# # Match with geographical data, create categories for mapping and drop unwanted variables
# Data_geog_WGS84 <- boroughs_WGS84%>% 
#   left_join(input_peopledata, by=c("GSS_CODE"="BoroughCode"))%>%
#   mutate(DispersalCat = cut(Rate_of_DA, breaks = c(-1, 0, 35, 70, 140, 300),
#                            labels = c("1", "2", "3", "4", "5"))) %>%
#   mutate(UASC_Colour = recode(UASC_Col, 
#                               "Green" = "1", 
#                               "Amber" = "2", 
#                               "Red" = "3", 
#                               "Purple" = "4")) %>%
#   mutate(PopCat = cut(Pop_total_2020, breaks = c(-1, 100000, 200000, 300000, 400000),
#                            labels = c("1", "2", "3", "4"))) %>%
#   select(!c("HECTARES", "BoroughName", "NONLD_AREA", "ONS_INNER", "SUB_2009", "SUB_2006")) 
# 
# # add unique ID to each row to help with matching
# Data_geog_WGS84 <- tibble::rowid_to_column(Data_geog_WGS84, "index")
# 
# # Create centroids for mapping using coordinates of lats and longs, and create index for matching  
# cent <- st_transform(Data_geog_WGS84, crs = 4326) %>%
#   st_centroid() %>% 
#   st_geometry() %>% 
#   as_tibble() %>% # convert list to tibble 
#   extract(geometry, c('long', 'lat'), '\\((.*), (.*)\\)', convert = TRUE) %>%
#   rowid_to_column("index")
# 
# # Merge original data file with new centroid data
# Data_geog_WGS84_cent <- merge(Data_geog_WGS84, cent, by="index")
# 
# # Convert data for use in DT and crosstalk
# shared_migration_data <- SharedData$new(Data_geog_WGS84_cent)
# 
# #--------------------------------------------------------------------------
# 
# ## Provide extra info for choropleth maps
# 
# # For dispersal map
# catblue5 = c('#eeeeee', '#a6bbd4', '#6e88a6', '#44586f', '#252c35')
# 
# catnames_new <- c("0", "1-34", "35 - 69", "70-139", "140-300")
# 
# mypalette2 <- colorFactor(catblue5,
#                           levels = c("1", "2", "3", "4", "5"),
#                           ordered = FALSE,
#                           na.color = "#808080",
#                           alpha = FALSE,
#                           reverse = FALSE)


```

Schools {data-icon="ion-home"}
=====================================  

### Primary and Secondary Schools (state-funded) headcount

Row {data-height=500}
-----------------------------------------------------------------------

### Line chart - Primary schools numbers over time

```{r chart1}

# chart

```

### Line chart - Secondary schools numbers over time

```{r chart2}

# chart

```

Row {data-height=500}
-----------------------------------------------------------------------

### Map - Primary schools change

```{r map1}

# map


```

### Map - Secondary schools change

```{r map2}

# map

```

Births and total fertility rate {data-navmenu="🕮 Births" data-icon="ion-stats-bars"}
=====================================  

### Births and total fertility rate

Row {data-height=500}
-----------------------------------------------------------------------

### Line chart - Births over time

```{r chart3}

# chart

```

### Line chart - TFR over time

```{r chart4}

#chart

```
Row {data-height=500}
-----------------------------------------------------------------------

### Line chart - Number of potential mothers over time

```{r chart5}

#chart

```
### Map - TFR now

```{r map3}

## Map for Dispersal accomodation

# dispersal_map <- leaflet(shared_migration_data) %>% 
#   setView(lng = -0.1181 , lat = 51.51, zoom = 9) %>% # 
#   addProviderTiles(providers$CartoDB.Positron) %>% 
#   addPolygons(fillColor = ~mypalette2(DispersalCat),
#                  weight = 0.5,
#                  opacity = 1,
#                  color = "black",
#                 fillOpacity = 0.7) %>%
#   addLegend("bottomleft", 
#             colors = catblue5, 
#             values = DispersalCat, 
#             labels = catnames_new, title = "Dispersed acc., Asylum seekers/100,000 residents") %>%
#   addAwesomeMarkers(data = shared_migration_data, 
#              lng =  ~ long, lat = ~ lat, 
#                popup = ~paste0(
#        "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
#       
#       "<table style='width:100%'>",
#       
#       "<tr>",
#       "<th>Number in dispersal</th>",
#       "<th>", Data_geog_WGS84_cent$SeekingAsylum_InDispersal,"</tr>",
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Borough population</th>",
#       "<th>", format(Data_geog_WGS84_cent$Pop_total_2020, big.mark = ",", scientific = FALSE)  ,
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Rate of dispersal accomodation<br>per 100,000 residents</th>",
#       "<th>", Data_geog_WGS84_cent$Rate_of_DA, "</tr>",
#       "</tr>"
#           ),  # end popup()
#     icon = awesomeIcons(
#       library = "ion",
#       icon = "ion-android-radio-button-on",
#       iconColor = "white",
#       markerColor = ifelse(
#         test = Data_geog_WGS84_cent$Inner == 1, 
#         yes = "red",
#         no = "blue")
#       )
#     )    # end addAwesomeMarkers()
# dispersal_map

```

Age specific fertility rate and Mean age at birth {data-navmenu="🕮 Births" data-icon="ion-connection-bars"}
=====================================  

### Age specific fertility rate and Mean age at birth

Row {data-height=500}
-----------------------------------------------------------------------

### Line chart - ASFR over time

```{r chart6}

# ASFR chart

```

### Line chart - SMA over time

```{r chart7}

# SMA chart

```
Row {data-height=500}
-----------------------------------------------------------------------

### Map - ASFR
 
```{r map4}
 
# UASC_map <- leaflet(shared_migration_data) %>% 
#   setView(lng = -0.1181 , lat = 51.51, zoom =9) %>% # 
#   addProviderTiles(providers$CartoDB.Positron) %>% 
#   addPolygons(fillColor = ~mypalette3(UASC_Colour),
#                  weight = 0.5,
#                  opacity = 0.8,
#                  color = "black",
#                 fillOpacity = 0.5) %>%
#   addLegend("bottomleft", 
#             colors = UASC_catcolor, 
#             values = UASC_Cat, 
#             labels = UASC_catnames , title = "UASC Categories: 0.07% Threshold")%>%
#   addAwesomeMarkers(data = shared_migration_data, 
#              lng =  ~ long, lat = ~ lat, 
#                popup = ~paste0(
#        "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
#       
#       "<table style='width:100%'>",
#       
#       "<tr>",
#       "<th>UASC in borough</th>",
#       "<th>", Data_geog_WGS84_cent$UASC,
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Borough <18 y.o. population</th>",
#       "<th>", format(Data_geog_WGS84_cent$Pop_child_2020, big.mark = ",", scientific = FALSE),
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Rate of UASC<br>per 100 children</th>",
#       "<th>", format(round(Data_geog_WGS84_cent$UASC_Rate, 2)), "</th>",
#       "</tr>"
#           ),  # end popup()
#     icon = awesomeIcons(
#       library = "ion",
#       icon = "ion-android-radio-button-on",
#       iconColor = "white",
#       markerColor = ifelse(
#         test = Data_geog_WGS84_cent$Inner == 1, 
#         yes = "red",
#         no = "blue")
#       )
#     )    # end addAwesomeMarkers()
# UASC_map

```
### Map - SMA
 
```{r map5}
# 
# UASC_map <- leaflet(shared_migration_data) %>% 
#   setView(lng = -0.1181 , lat = 51.51, zoom =9) %>% # 
#   addProviderTiles(providers$CartoDB.Positron) %>% 
#   addPolygons(fillColor = ~mypalette3(UASC_Colour),
#                  weight = 0.5,
#                  opacity = 0.8,
#                  color = "black",
#                 fillOpacity = 0.5) %>%
#   addLegend("bottomleft", 
#             colors = UASC_catcolor, 
#             values = UASC_Cat, 
#             labels = UASC_catnames , title = "UASC Categories: 0.07% Threshold")%>%
#   addAwesomeMarkers(data = shared_migration_data, 
#              lng =  ~ long, lat = ~ lat, 
#                popup = ~paste0(
#        "<h4>", Data_geog_WGS84_cent$NAME, "</h4>",
#       
#       "<table style='width:100%'>",
#       
#       "<tr>",
#       "<th>UASC in borough</th>",
#       "<th>", Data_geog_WGS84_cent$UASC,
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Borough <18 y.o. population</th>",
#       "<th>", format(Data_geog_WGS84_cent$Pop_child_2020, big.mark = ",", scientific = FALSE),
#       "</tr>",
#       
#       "<tr>",
#       "<tr>",
#       "<th>Rate of UASC<br>per 100 children</th>",
#       "<th>", format(round(Data_geog_WGS84_cent$UASC_Rate, 2)), "</th>",
#       "</tr>"
#           ),  # end popup()
#     icon = awesomeIcons(
#       library = "ion",
#       icon = "ion-android-radio-button-on",
#       iconColor = "white",
#       markerColor = ifelse(
#         test = Data_geog_WGS84_cent$Inner == 1, 
#         yes = "red",
#         no = "blue")
#       )
#     )    # end addAwesomeMarkers()
# UASC_map

```

Migration  {data-icon="ion-person-stalker"}
=====================================  

### Migration statistics from MYE 2022

Column {data-width=500}
-----------------------------------------------------------------------

### Domestic migration

```{r chart8}

## Dom mig numbers from MYE


```

### International migration


```{r chart9}

### Int mig numbers from MYE 2022

```

Total population {data-icon="ion-home"}
=====================================  

### Total population of young children


Row {data-height=500}
-----------------------------------------------------------------------

### Map - Change in population 0 - 10

```{r map6}


# Map - Change in population 0 - 10

```

### Map - Change in HH with more than 1 dependent child

```{r map7}

# Map - Change in HH with more than 1 dependent child

```

Row {data-height=500}
-----------------------------------------------------------------------

### Map - Another topic

```{r map8}
# another map


```

### Map - Another topic

```{r map9}

# another map

```